### 2018-01-25 master/paper.tex
Fix the parts pointed out

\usepackage[dvipdfmx]{graphicx}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{color}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small\ttfamily},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
The proposed framework enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
In addition, this paper proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.

@@

This chapter describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
The following section explains TECS, mruby, and mruby on TECS framework.

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/SystemModel.pdf}
    \caption{System model of the proposed framework}
    \label{fig:SystemModel}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsection{Component Model}
Fig.\ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes, and variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\begin{description}
    \item[{\bf Signature Description}]
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    void initializePort( [in]int32_t type );
    ER setPower( [in]int power );
    ER stop( [in]bool_t brake );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/TECSFlow.pdf}
    \caption{Development flow using TECS}
    \label{fig:TECSFlow}
\end{figure}

Fig.\ref{fig:TECSFlow} shows the development flow using TECS.
TECS generator generates the interface code (.H and .C) and the configure file of the RTOS (.cfg) from the CDL file.

@@

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Fig.\ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/mruby.pdf}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

@@

\subsection{System Model of mruby on TECS}
% The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.
An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.

@@

Fig.\ref{fig:mrubyTECSbridge} illustrates an mruby-TECS bridge used to control a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/mrubyTECSbridge.pdf}
\caption{mruby-TECS bridge}
\label{fig:mrubyTECSbridge}
\end{figure}

The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.

@@

Fig.\ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
Users send and receive data using a Communication End Point (CEP), an interface that functions like a socket.
In the transmission process, headers are attached to the data body passed to the CEP at each protocol layer before the data are transmitted from the network device.
In the reception process, the headers of the data bodies received by the network device are analyzed at each protocol layer, and the data are then passed to the CEP.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

The components of the TINET+TECS protocol stack are shown in Fig.\ref{fig:ComponentProtocolStack}.
Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and functionalities such as input/output functions are defined as respective components.
By using such small grain components, software visibility is improved.
The components of each protocol are described as follows.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of a protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

@@

The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig.\ref{fig:tMemoryAllocator}.
tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and releasing memory areas of a requested size. 
tFixedSizeMemoryPool components of various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
On the other hand, all components that need to allocate or deallocate memory, e.g., tTCPInput and tEthernetOutput, connect to the memory allocator component.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

\item {\it send} is another specifier for transferring data to a callee from a caller.
The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
In the case of the {\it in} specifier, both allocating and deallocating of the data memory are performed in the caller.
By contrast, in the case of {\it send}, the caller allocates the data memory and the callee deallocates it.

@@

\item {\it receive} is another specifier for a caller receiving data from a callee.
The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
In the case of {\it out}, the callee writes data in the memory allocated by a caller, whereas in the {\it receive} case, the callee allocates the data memory.
Deallocating of the memory is performed in the caller in both cases.
\end{itemize}

As shown in Fig.\ref{src:SendReceive}, sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
Developers hardly make mistakes of memory operation because these specifiers completely pass an ownership of memory.
Common object request broker architecture (CORBA) does not consider memory sharing; CORBA has no functionalities
such as {\it send}/{\it receive}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig.\ref{fig:DynamicConnection}) as a new functionality.
In Fig.\ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig.\ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

To utilize dynamic connectivity, a selector should be defined.
A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig.\ref{src:DynamicCDLcode}).
{\it [ref\_desc]} is used to identify call ports referring to descriptors. 
In the case of Fig.\ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.

@@

Fig.\ref{src:DynamicCcode} shows a sample code of the dynamic connection.
The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for a connection request.
The dynamic connection in the function is performed as shown in Fig.\ref{src:DynamicCcode}.
First, the descriptor of REP to be joined is obtained (Line 3 in Fig.\ref{src:DynamicCcode}).
The first argument, {\it \&desc}, is a variable used to store the descriptor information, whereas the second argument, {\it repid}, is the index of tREP cells.
Next, the descriptor is set (Line 5 in Fig.\ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig.\ref{src:DynamicCcode}).

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/TECSAdapter.pdf}
    \caption{TECS adapter}
    \label{fig:TECSAdapter}
\end{figure}

Since existing communication programs are supported, a communication task can be applied without porting, and other tasks can be developed with mruby program.

@@

TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system proposed by M. Masmano et al.
TLSF memory allocator has the following features.

@@

TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
The overview of TLSF algorithm is shown in Fig.\ref{fig:TLSF}.
Consider a case where a request, $malloc(100)$, is called to allocate a memory.
First, it is classified by the most significant bit of the requested memory size.
In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
Second, it is further classified.
In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
Free block\footnote{Free block is an available memory block.} in this range is used.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/TLSF.pdf}
    \caption{TLSF Algorithm}
    \label{fig:TLSF}
\end{figure}

@@

This section describes the component design of TLSF memory allocator.
In this research, we are using TECS to componentize TLSF.
The version of TLSF used is 2.4.6\footnote{http://www.gii.upv.es/tlsf/main/repo}.

@@

Fig.\ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signature.

@@

The celltype description of the TLSF memory allocator component is shown in Fig.\ref{src:TLSFCelltype}.
An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
Here, {\it [inline]} is a specifier for Implementation as inline functions.
A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
Each component holds own heap area.
Therefore, even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/WithoutTECS.pdf}
    \caption{TLSF before componentization}
    \label{fig:WithoutTECS}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/WithTECS.pdf}
    \caption{TLSF after componentization}
    \label{fig:WithTECS}
\end{figure}

As shown in Fig.\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
In the research, TLSF is componentized using TECS as shown in Fig.\ref{fig:WithTECS}.
It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/UseCase_mruby.pdf}
    \caption{Component description of RiteVM and TLSF+TECS}
    \label{fig:UseCase_mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/UseCase_TINET.pdf}
    \caption{Fixed-size and TLSF memory allocator components}
    \label{fig:UseCase_TINET}
\end{figure}

>>>>

\usepackage[dvipdfmx]{graphicx}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{color}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small\ttfamily},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

@@

High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
The proposed framework enables that mruby programs call TINET, a TCP/IP protocol stack for use in embedded systems, functions.
In addition, this paper proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.
Moreover, the TLSF+TECS functionality which obtains statistical information of mruby VM's memory usage helps developers debug and verify the systems.

@@

This chapter describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
The following section explains TECS, mruby, and mruby on TECS framework.

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/SystemModel.pdf}
    \caption{System model of the proposed framework}
    \label{fig:SystemModel}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsection{Component Model}
Fig. \ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes, and variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\begin{description}
    \item[{\bf Signature Description}]
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig. \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    void initializePort( [in]int32_t type );
    ER setPower( [in]int power );
    ER stop( [in]bool_t brake );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig. \ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]
        The build description is used to instantiate and connect {\it cell}s.
        Fig. \ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig. \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/TECSFlow.pdf}
    \caption{Development flow using TECS}
    \label{fig:TECSFlow}
\end{figure}

Fig. \ref{fig:TECSFlow} shows the development flow using TECS.
TECS generator generates the interface code (.H and .C) and the configure file of the RTOS (.cfg) from the CDL file.

@@

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Fig. \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/mruby.pdf}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

@@

\subsection{System Model of mruby on TECS}
% The present mruby on TECS system model is shown in Fig. \ref{fig:mrubyonTECS}.
Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.
An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.

@@

Fig. \ref{fig:mrubyTECSbridge} illustrates an mruby-TECS bridge used to control a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/mrubyTECSbridge.pdf}
\caption{mruby-TECS bridge}
\label{fig:mrubyTECSbridge}
\end{figure}

@@

Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
Users send and receive data using a Communication End Point (CEP), an interface that functions like a socket.
In the transmission process, headers are attached to the data body passed to the CEP at each protocol layer before the data are transmitted from the network device.
In the reception process, the headers of the data bodies received by the network device are analyzed at each protocol layer, and the data are then passed to the CEP.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

@@

The components of the TINET+TECS protocol stack are shown in Fig. \ref{fig:ComponentProtocolStack}.
Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and functionalities such as input/output functions are defined as respective components.
By using such small grain components, software visibility is improved.
The components of each protocol are described as follows.

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of a protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

@@

The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig. \ref{fig:tMemoryAllocator}.
tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and releasing memory areas of a requested size. 
tFixedSizeMemoryPool components of various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
On the other hand, all components that need to allocate or deallocate memory, e.g., tTCPInput and tEthernetOutput, connect to the memory allocator component.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

\item {\it send} is another specifier for transferring data to a callee from a caller.
The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig. \ref{fig:SendReceive}.
In the case of the {\it in} specifier, both allocating and deallocating of the data memory are performed in the caller.
By contrast, in the case of {\it send}, the caller allocates the data memory and the callee deallocates it.

@@

\item {\it receive} is another specifier for a caller receiving data from a callee.
The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig. \ref{fig:SendReceive}.
In the case of {\it out}, the callee writes data in the memory allocated by a caller, whereas in the {\it receive} case, the callee allocates the data memory.
Deallocating of the memory is performed in the caller in both cases.
\end{itemize}

As shown in Fig. \ref{src:SendReceive}, sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
Developers hardly make mistakes of memory operation because these specifiers completely pass an ownership of memory.
Common object request broker architecture (CORBA) does not consider memory sharing; CORBA has no functionalities
such as {\it send}/{\it receive}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.

TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

To utilize dynamic connectivity, a selector should be defined.
A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig. \ref{src:DynamicCDLcode}).
{\it [ref\_desc]} is used to identify call ports referring to descriptors. 
In the case of Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.

@@

Fig. \ref{src:DynamicCcode} shows a sample code of the dynamic connection.
The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for a connection request.
The dynamic connection in the function is performed as shown in Fig. \ref{src:DynamicCcode}.
First, the descriptor of REP to be joined is obtained (Line 3 in Fig. \ref{src:DynamicCcode}).
The first argument, {\it \&desc}, is a variable used to store the descriptor information, whereas the second argument, {\it repid}, is the index of tREP cells.
Next, the descriptor is set (Line 5 in Fig. \ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig. \ref{src:DynamicCcode}).

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/TECSAdapter.pdf}
    \caption{TECS adapter}
    \label{fig:TECSAdapter}
\end{figure}

Since existing communication programs are supported, a communication task can be applied without porting, and other tasks can be developed with mruby programs.

@@

TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system.
TLSF memory allocator has the following features.

@@

TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
The overview of TLSF algorithm is shown in Fig. \ref{fig:TLSF}.
Consider a case where a request, $malloc(100)$, is called to allocate a memory.
First, it is classified by the most significant bit of the requested memory size.
In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
Second, it is further classified.
In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
Free block\footnote{Free block is an available memory block.} in this range is used.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/TLSF.pdf}
    \caption{TLSF Algorithm}
    \label{fig:TLSF}
\end{figure}

@@

This section describes the component design of TLSF memory allocator.
In this research, TECS is used to componentize TLSF.
The version of TLSF used is 2.4.6\footnote{http://www.gii.upv.es/tlsf/main/repo}.

@@

Fig. \ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signature.

@@

The celltype description of the TLSF memory allocator component is shown in Fig. \ref{src:TLSFCelltype}.
An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
Here, {\it [inline]} is a specifier for Implementation as inline functions.
A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
Each component holds own heap area.
Therefore, even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/WithoutTECS.pdf}
    \caption{TLSF before componentization}
    \label{fig:WithoutTECS}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/WithTECS.pdf}
    \caption{TLSF after componentization}
    \label{fig:WithTECS}
\end{figure}

As shown in Fig. \ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
In the research, TLSF is componentized using TECS as shown in Fig. \ref{fig:WithTECS}.
It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/UseCase_mruby.pdf}
    \caption{Component description of RiteVM and TLSF+TECS}
    \label{fig:UseCase_mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=12cm,clip]{figure/UseCase_TINET.pdf}
    \caption{Fixed-size and TLSF memory allocator components}
    \label{fig:UseCase_TINET}
\end{figure}
